Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-07 journal paper/content/related_work.tex
Minor edit.

The earlier work by \citet{bergemann1997market,bergemann2000experimentation} studies competition on both prices and quality, and allows for the data externality mentioned above. Specifically, the ``entrant" firm offers a new product of unknown quality, which is ``explored" if and only if the entrant attracts customers. However, because the entrant can only control the prices but not the product itself, the nature of exploration is fundamentally different. First, the goal of exploration is to reveal information about a fixed product. Second, the entrant can only affect the \emph{quantity} of the said information, but not \emph{which} information is being revealed. Third, revealing \emph{more} information is not necessarily better for the entrant (if the product's quality is actually low). Fourth, the social planner's exploration problem is very different from the firms'.%
\footnote{The planner faces a two-armed bandit problem, rather than a pricing problem. This is because the planner can directly choose a firm for each agent (by choosing a very low price for this firm, and a very high price for the other firm, because payments cancel out in social welfare).}
Consequently, when one compares competition to the planner, one can compare the outcomes but not the algorithms.

>>>>

The earlier work by \citet{bergemann1997market,bergemann2000experimentation} studies competition on both prices and quality, and allows for the data externality mentioned above. Specifically, the ``entrant" firm offers a new product of unknown quality, which is ``explored" if and only if the entrant attracts customers. However, because the entrant can only control the prices but not the product itself, the nature of exploration is fundamentally different. First, the goal of exploration is to reveal information about a fixed product. Second, the entrant can only affect the \emph{quantity} of the said information, but not \emph{which} information is being revealed. Third, revealing \emph{more} information is not necessarily better for the entrant (if the product's quality is actually low). Fourth, the social planner's exploration problem is very different from the firms'.%
\footnote{The planner faces a two-armed bandit problem, rather than a pricing problem. This is because the planner can directly choose a firm for each agent (by choosing a very low price for this firm, and a very high price for the other).}
% firm, because payments cancel out in social welfare).}
Consequently, when one compares competition to the planner, one can compare the outcomes but not the algorithms.
